LAGOS lake depth

### 2020-01-06 figures/00_maps.Rmd
add proportion labels

ggplot() + 
  geom_sf(data = dt_plot, aes(fill = prop_maxdepth)) + 
  labs(fill = "") +
  coord_sf(datum = NA) + theme_void()

>>>>

# add text labels of proportions

ggplot() + 
  geom_sf(data = dt_plot, aes(fill = prop_maxdepth)) + 
  geom_sf_text(data = dt_plot, 
               aes(label = round(prop_maxdepth, 2)), 
               size = 2.5) +
  labs(fill = "") +
  coord_sf(datum = NA) + theme_void()
